Reconstructing the Lensing Mass in the Universe \\ from Photometric Catalog Data

### 2012-11-01 doc/paper-lcr.tex
added citations to Karpenka et al

The probability density function (PDF) for the external convergence
given our available data $\data$, $\Pr(\xkappa|\data)$,  is the  key
quantity we seek, since by marginalising over this distribution we can
correctly propagate the uncertainties due to line-of-sight perturbations
(as \citeauthor{FadelyEtal2009} did).  
%
\citet{GunnarssonEtal2006} investigated a related PDF,  for the
magnification, using a galaxy halo model. Applying empirical galaxy
scaling relations both to simulate mock catalogs and then to reconstruct
the line of sight mass distribution. While they did not explore highly
overdense lines of sight, or the impact of groups and clusters, they
found that under their simplifying assumptions, the dispersion in
apparent source brightness due to lensing magnification could be reduced
by a factor of two.
%
\citet{WongEtal2011} estimated the PDF for the external shear,
$\Pr(\gamma|\data)$ from their survey data, running similar Monte Carlo
reconstructions of the mass in nine lens fields based on
\citeauthor{WilliamsEtal2006} and \citeauthor{MomchevaEtal2006}'s
photometric and spectroscopic measurements of galaxies close to the line
of sight. They then  compared the resulting predicted shear
distributions with the external shear demanded by the strong lens model.
Their reconstructions showed most of the shear to have been generated by
bright galaxies within 2~arcminutes of the lens, and that both line of
sight structures and the group of galaxies in each lens plane contribute
significant proportions of the shear. They found significant
discrepancies between the lens model shear and the Monte Carlo
predictions, but were unable to distinguish between the environment
modelling and the strong lens modelling as the cause of these
discrepancies.

@@

In this paper, we combine the halo model reconstruction approach of
\citeauthor{GunnarssonEtal2006} and \citeauthor{WongEtal2011}, with the
idea of calibrating to simulations from \citeauthor{SuyuEtal2010}, in
order to put the halo model for  estimating the weak lensing convergence
due to mass along the line of sight to a distant source into a sound
framework for evaluating this important source of systematic
uncertainty, as we look forward to ever increasing sample sizes and
statistical precision. Taking the $\kappa$ values from
\citeauthor{HilbertEtal2009}'s ray-tracing calculations as the ``truth''
that we have to recover, we use the \MS mock galaxy catalogs first to
{\it calibrate} the reconstruction, and account for unseen mass and
voids, and then to {\it test} the accuracy of the line of sight mass
reconstruction under this assumption. Probabilistically assigning mass
and redshift to every observed galaxy in a given observed field, we
generate Monte Carlo sample line of sight mass distributions, and so
construct the PDF $\Pr(\kappa|\data)$ for that field. We then emulate
the combination of many such PDFs to quantify the residual biases that
would be translated to the global (including cosmological) parameters.
In doing so, we aim to answer the following questions:

@@

Strong lenses sit in our real Universe -- they are not \truely isolated;
there is some mass along the line of sight coming from intervening
structures. These structures may be physically associated with the lens
e.g. other members of a group or cluster, or they may be the result of
chance alignments at any redshift.  Whilst it is rare for three galaxies
to line up well enough for both of the background sources to be strongly
lensed \citep{GavazziEtal2008,CollettEtal2012a}, the large size of dark
matter halos makes a partial alignment -- with the additional structure
acting as a perturbing weak lens --  a near certainty
\citep{Vale+White2003,HilbertEtal2007}. These additional structures
induce an external shear which can be recovered in the mass-modelling of
the lens, but they can also introduce a convergence that is undetectable
from the image positions, shapes and relative fluxes
\citep{FalcoEtal1985}.

If the intrinsic source brightness changes, the observed brightness in
each image does not change simultaneously: there will be a time delay,
$\Delta t$, between the brightness change in each image. Despite the
invariance of the image positions and fluxes, under the addition of an
external convergence (and appropriate re-scaling of the lens potential)
the relative Fermat potential between the images is {\it not} invariant,
and so the time delay changes. As such it is necessary to include
$\kappa$ in the lens modelling, if cosmological parameters are to be
estimated accurately and precisely from observed time delays
\citep{SuyuEtal2010}. Mass distributions that are physically associated with the lens galaxy
will affect the stellar dynamics of the lens galaxy, so that dynamical
observations can break the internal mass-sheet degeneracy by providing
an additional estimate of the lens galaxy's mass
\citep[e.g.,][]{SuyuEtal2010}. In this work our aim is to quantify the
lensing effect of massive objects, regardless of their position along
the line of sight.

@@

The relationship between convergence $\kappa$ and magnification $\mu$ is
\bea 
\mu &=&       \frac{1}{(1-\kappa)^2 - |\gamma|^2}, \notag \\
    &\approx& (1+2\kappa)
\label{eq:MassSheet:mag}
\eea
where we have used the facts that the magnitude of the gravitational
shear at any point is typically comparable to the magnitude of the 
convergence, and that both are typically small. 
Under these assumptions, the fractional uncertainty in the
inferred luminosity of a magnified source will be approximately  twice
the absolute uncertainty in the convergence~$\kappa$. These
relationships will allow us to put our results on convergence estimation
in context.

@@

One of the goals of this paper is to define a method for estimating the
convergence at any point on the sky, given a   catalog of observed
galaxy positions and properties. Typically this could be a  photometric
galaxy catalog, containing positions, brightnesses, colours, and
possibly stellar masses and redshifts for each galaxy in the field of
the lens, down to some magnitude limit. Since we cannot observe the
surface mass density of each halo directy, we need some way of
estimating the mass of each halo in the catalog, so that we can compute
its contribution to the total $\kappa$ along the line of sight \citep[as
in \eg][]{GunnarssonEtal2006,WongEtal2011}. This mass assignment recipe
will be uncertain, but can be calibrated with cosmological simulations.

@@

If one integrates the density profile of an NFW profile out to infinite
radius, the total mass diverges. Similarly, if the universe is
homogeneously populated with NFW halos, the projected surface mass along
any line of sight will also be divergant.\footnote{At large radius,
$\Sigma_{\rm nfw} \propto R^{-2}$, but the differential number of halos
centred within an annulus of width $\dee R$ is given by $\dee N_{\rm
annulus} \propto R \dee R$, so  $\Sigma_{\rm total} \propto
\int_{0}^{\infty} R^{-1} \dee R$, which diverges logarithmically} Since
infinite mass is unphysical, the profile must be truncated at some
point. Several truncation profiles have been suggested
\citep[e.g][]{BMO}, but beyond several virial radii, the amount of
matter associated with a halo is likely to be low. In this work we
assume the truncated NFW profile
\be\label{eq:bmoprofile}
\rho(r) = 
\frac{\rho_{\rm NFW} (r)}{1+\left(r/r_{t}\right)^2},
\ee
which is the same as the NFW profile in the limit that the truncation
radius, $r_t$ goes to infinity. We use a truncation radius of five times
the virial radius, but our results are robust for any choice of $r_t>2
\times r_{200}$. The formula for the projected surface mass density 
$\Sigma(D_{od}\theta)$ for this
mass profile is given in \citet{BMO}.

@@

This PDF contains a hidden assumption of an uninformative prior PDF for
$\kappah$ -- in the case of infinitely poorly measured stellar masses and
redshifts, $\pr(\kappah|\data)$ will have very long tails corresponding to
very overdense sightlines that we do not believe exist. The resolution of this
is to divide out the effective prior PDF that was applied during the halo mass
estimation process (which is broad, and hance close to uniform), and apply an
additional prior on $\kappah$, given by the global underlying $\kappah$
distribution from the simulation. In the limiting  case of very poor
photometric data, $\pr(\kappah|\data)$ then defaults to this distribution.

@@

We have shown that reconstructing the matter due to halos along any line
of sight can improve the constraints on the external convergence along
that line of sight. The total convergence along a line of sight is
strongly correlated with the reconstructed $\kappah$. However since our
model ignores voids and assumes all halos follow a spherical
truncated-NFW profile our halo model does not include all of the relevant
physics; hence, the width of our resulting $\pr(\kappa|\data)$ is still
typically $\sim$0.01 for any given lightcone, even with a perfect
knowledge of every halo's virial mass and redshift. To make further
progress a more advanced treatment of both voids and halos will be
necessary. Interestingly, we have found that the most empty lines of
sight can be reconstructed with the most precision. $\kappa$ estimates
for empty
lines of sight receive few contributions from halos, and a large
contribution from voids; since they have the tightest PDFs after the
reconstruction it seems that our model's biggest uncertainties are
driven by naively reconstructing halos rather than neglecting voids.
With a photometric reconstruction of the field there is a significant
broadening, but the resulting precision is still typically 50\% 
higher than using the global $\kappa$ distribution.

@@

More generally, the method presented here is tied to the simulations at
several points: in particular, the prior PDF for $\kappah$, and the
conditional distribution $\pr(\kappa|\kappah)$ used to convert halo model
convergence to total convergence. The former tie could potentially be avoided
if the halo mass estimation gave rise to a reasonable $\pr(\kappah|\data)$ on
its own. Possibilities for improving the precision of the halo mass estimation
include incorporating a group and cluster finder, and then inferring halo mass
from optical richness \citep[\eg][]{MaxBCG} in tandem with BCG stellar mass,
and using additional galaxy scaling relations to make use of the luminosity
and size information present. The latter tie is more difficult, since breaking
it means modelling the unseen mass structures and voids from first principles.
In the wide field survey era, will it be possible to infer hierarchically the
parameters of a flexible model for these things from the data itself? Weak
lensing shears will be available over the whole Euclid and LSST survey areas:
constraining halo models using this information is an interesting possibility.

@@

\item Our halo model uses a truncated spherical NFW profile for each dark
matter halo and neglects voids, but despite the model's simplicity the
reconstructed $\kappah$ is a good, if biased, tracer of $\kappa$.  We found
that with perfect knowledge of the halo mass and redshift (from the Millennium
Simulation catalogs), for a typical line of sight the reconstruction gives an
unbiased estimate of $\kappa$ that is a factor of 2 more precise than the
global $\pr(\kappa)$.

@@

\item  For the most overdense lines of sight, the reconstruction produces a
very broad PDF, but since the reconstruction can be performed before follow-up
time is invested it will be possible to discard the most uncertain lines of
sight and optimize the use of follow-up time. Photometric data is sufficient 
to select the best lines of sight for follow-up. Spectroscopic coverage helps
to tighten  $\pr(\kappa|\data)$ for high $\kappa$ lines of sight, but is of
limited use for  low $\kappa$ lines of sight.

\item It is very rare for halos further than 2 arcminutes from the line of
sight to make a significant contribution to $\pr(\kappa|\data)$. We also found
that including halos whose host galaxy is less luminous than $i=24$ does not
significantly improve our reconstruction precision. A photometric survey to
this depth of a 4$\times$4 arcminute patch around the lens would approach the
limiting uncertainties of our simple reconstruction recipe, and yield a 
$\pr(\kappa|\data)$ that has, on average, a width of 0.016. This is 1.5 times
less broad than the global $\pr(\kappa)$.

\item We find that the lines of sight with the sharpest inferred
$\pr(\kappa|\data)$ are typically under-dense. With a photometric
reconstruction of all lens fields, and following up only the lenses with the
most precise $\kappa$ estimates, the width of the dominant statistical
uncertainty in time-delay cosmography can be halved, without inducing biases
at the one percent level.

@@

External convergence is not the only uncertainty in time delay cosmology,
but for systems like B1608 it is the dominant one. For most lines
of sight it is likely that lens modelling induces uncertainties at the
$\sim$3 percent level, which far exceeds the typical $\kappa$ uncertainties
after applying our reconstruction \proceedure. By using our method to
reconstruct lines of sight and select which lense are followed-up, the
uncertainties due to line of sight convergence will become a sub-dominant 
source of error.

>>>>

The probability density function (PDF) for the external convergence
given our available data $\data$, $\Pr(\xkappa|\data)$,  is the  key
quantity we seek, since by marginalising over this distribution we can
correctly propagate the uncertainties due to line-of-sight perturbations
(as \citeauthor{FadelyEtal2009} did).  
%
\citet{GunnarssonEtal2006} investigated a related PDF,  for the
magnification, using a galaxy halo model. Applying empirical galaxy
scaling relations both to simulate mock catalogs and then to reconstruct
the line of sight mass distribution. While they did not explore highly
overdense lines of sight, or the impact of groups and clusters, they
found that under their simplifying assumptions, the dispersion in
apparent source brightness due to lensing magnification could be reduced
by a factor of two.
%
\citet{WongEtal2011} estimated the PDF for the external shear,
$\Pr(\gamma|\data)$ from their survey data, running similar Monte Carlo
reconstructions of the mass in nine lens fields based on
\citeauthor{WilliamsEtal2006} and \citeauthor{MomchevaEtal2006}'s
photometric and spectroscopic measurements of galaxies close to the line
of sight. They then  compared the resulting predicted shear
distributions with the external shear demanded by the strong lens model.
Their reconstructions showed most of the shear to have been generated by
bright galaxies within 2~arcminutes of the lens, and that both line of
sight structures and the group of galaxies in each lens plane contribute
significant proportions of the shear. They found significant
discrepancies between the lens model shear and the Monte Carlo
predictions, but were unable to distinguish between the environment
modelling and the strong lens modelling as the cause of these
discrepancies.
%
\citet{KarpenkaEtal2012} used a halo model to predict the magnification due to
galaxies along the line of sight to type Ia supernovae, and inferred the
parameters of the scaling relations between light and mass in these galaxies
from hundreds of supernova lightcone simultaneously. Following
\citet{JonssonEtal2010}, they subtract off the mean convergence to ensure that
the universal mass budget is balanced, and compare models where the halos are
all have either truncated singular isothermal profiles, or 
NFW profiles. Both groups detect lensing effects in the supernova data.

@@

In this paper, we combine the halo model reconstruction approach of
\citeauthor{GunnarssonEtal2006}, \citeauthor{JonssonEtal2010}, 
\citeauthor{WongEtal2011} and others, with the
idea of calibrating to simulations from \citeauthor{SuyuEtal2010}, in
order to put the halo model for  estimating the weak lensing convergence
due to mass along the line of sight to a distant source into a sound
framework for evaluating this important source of systematic
uncertainty, as we look forward to ever increasing sample sizes and
statistical precision. Taking the $\kappa$ values from
\citeauthor{HilbertEtal2009}'s ray-tracing calculations as the ``truth''
that we have to recover, we use the \MS mock galaxy catalogs first to
{\it calibrate} the reconstruction, and account for unseen mass and
voids, and then to {\it test} the accuracy of the line of sight mass
reconstruction under this assumption. Probabilistically assigning mass
and redshift to every observed galaxy in a given observed field, we
generate Monte Carlo sample line of sight mass distributions, and so
construct the PDF $\Pr(\kappa|\data)$ for that field. We then emulate
the combination of many such PDFs to quantify the residual biases that
would be translated to the global (including cosmological) parameters.
In doing so, we aim to answer the following questions:

@@

Strong lenses, type Ia supernovae and other cosmologically interesting objects
are never viewed unlensed: 
there is some mass along the line of sight to them coming from intervening
structures. These structures may be physically associated with the target
e.g. other members of a group or cluster, or they may be the result of
chance alignments at any redshift.  
% While it is rare for three galaxies
% to line up well enough for both of the background sources to be strongly
% lensed \citep{GavazziEtal2008,CollettEtal2012a}, 
The large size of dark
matter halos makes partial alignments -- such that they
act as perturbing weak lenses --  a near certainty
\citep{Vale+White2003,HilbertEtal2007}. These additional structures
induce an external shear which can be recovered in the mass-modelling of
a strong lens, but they also introduce a convergence that is undetectable even
in these systems:
the lensed image positions, shapes and relative fluxes are affected, but not
in an unambiguous way
\citep{FalcoEtal1985}.

In time delay lens systems, under the addition of an external convergence (and
appropriate re-scaling of the lens potential) the relative Fermat potential
between the images is {\it not} invariant. This means that the time delay
between the images changes, despite the invariance of the image positions and
fluxes. As such it is necessary to include $\kappa$ in the lens modelling, if
cosmological parameters are to be estimated accurately and precisely from
observed time delays \citep{SuyuEtal2010}. Mass distributions that are
physically associated with the lens galaxy will affect the stellar dynamics of
the lens galaxy, so that dynamical observations can break the internal
mass-sheet degeneracy by providing an additional estimate of the lens galaxy's
mass \citep[e.g.,][]{SuyuEtal2010}. In this work our aim is to quantify the
lensing effect of massive objects, regardless of their position along the line
of sight.

@@

For type Ia supernovae, it is the magnification due to line of sight mass
structure that is a potential source of cosmographic error.
The relationship between convergence $\kappa$ and magnification $\mu$ is
\bea 
\mu &=&       \frac{1}{(1-\kappa)^2 - |\gamma|^2}, \notag \\
    &\approx& (1+2\kappa)
\label{eq:MassSheet:mag}
\eea
where we have used the facts that the magnitude of the gravitational
shear at any point is typically comparable to the magnitude of the 
convergence, and that both are typically small. 
Under these assumptions, the fractional uncertainty in the
inferred luminosity of a magnified source will be approximately  twice
the absolute uncertainty in the convergence~$\kappa$. These
relationships will allow us to put our results on convergence estimation
in context.

@@

We require a method for estimating the
convergence at any point on the sky, given a catalog of observed
galaxy properties such as positions, brightnesses, colours, and
possibly stellar masses and redshifts, for every galaxy in the field of
the lens, down to some magnitude limit. Since we cannot observe the
surface mass density of each halo directy, we need some way of
estimating the mass of each halo in the catalog, so that we can compute
its contribution to the total $\kappa$ along the line of sight \citep[as
in \eg][]{GunnarssonEtal2006,WongEtal2011,KarpenkaEtal2012}. 
This mass assignment recipe
will be uncertain, but can be calibrated with cosmological simulations, which
represent a significant additional source of information to what is present in
the data.

@@

If one integrates the density profile of an NFW profile out to infinite
radius, the total mass diverges. Similarly, if the universe is
homogeneously populated with NFW halos, the projected surface mass along
any line of sight will also be divergent.\footnote{At large radius,
$\Sigma_{\rm nfw} \propto R^{-2}$, but the differential number of halos
centred within an annulus of width $\dee R$ is given by $\dee N_{\rm
annulus} \propto R \dee R$, so  $\Sigma_{\rm total} \propto
\int_{0}^{\infty} R^{-1} \dee R$, which diverges logarithmically} Since
infinite mass is unphysical, the profile must be truncated at some
point. Several truncation profiles have been suggested
\citep[e.g][]{BMO}, but beyond several virial radii, the amount of
matter associated with a halo is likely to be low. In this work we
assume the truncated NFW profile
\be\label{eq:bmoprofile}
\rho(r) = 
\frac{\rho_{\rm NFW} (r)}{1+\left(r/r_{t}\right)^2},
\ee
which is the same as the NFW profile in the limit that the truncation
radius, $r_t$ goes to infinity. We use a truncation radius of five times
the virial radius, but our results are robust for any choice of $r_t>2
\times r_{200}$. The formula for the projected surface mass density 
$\Sigma(D_{od}\theta)$ for this
mass profile is given in \citet{BMO}.

@@

This PDF contains a hidden assumption of an uninformative prior PDF for
$\kappah$ -- in the case of infinitely poorly measured stellar masses and
redshifts, $\pr(\kappah|\data)$ will have very long tails corresponding to
very overdense sightlines that we do not believe exist. The resolution of this
is to divide out the effective prior PDF that was applied during the halo mass
estimation process (which is broad, and hence close to uniform), and apply an
additional prior on $\kappah$, given by the global underlying $\kappah$
distribution from the simulation. In the limiting  case of very poor
photometric data, $\pr(\kappah|\data)$ then defaults to this distribution.

@@

We have shown that reconstructing the matter due to halos along any line
of sight can improve the constraints on the external convergence along
that line of sight. The total convergence along a line of sight is
strongly correlated with the reconstructed $\kappah$. However since our
model ignores voids and assumes all halos follow a spherical
truncated-NFW profile our halo model does not include all of the relevant
physics; hence, the width of our resulting $\pr(\kappa|\data)$ is still
typically $\sim$0.01 for any given lightcone, even with a perfect
knowledge of every halo's virial mass and redshift. To make further
progress a more advanced treatment of both voids and halos will be
necessary. \citet{KarpenkaEtal2012} find that their supernova data prefer, in
the context of their simple halo model, a truncated isothermal profile for the
galaxy mass distributions. Weak galaxy-galaxy and cluster-galaxy 
lensing studies
\citep[\eg][]{GavazziEtal2006,JohnsonEtal2007} also suggest an approximately
isothermal profile for the mass-shear correlation function; however, at large
radii these profiles are dominated by the effects of neighbouring halos, which
should be taken into account by our model. Further iterations on the analysis
presented here should include the stellar mass distributions that cause the
isothermal density profiles in the centres of galaxies, although we do not
expect this to have a big impact on the model. Likewise,  halo
ellipticity may have some small effect on the predicted convergence.

Filaments and voids are more difficult to model, but simple forms could in
principle be derived from the structures found in the simulations, and
included in the halo model in some way. Most importantly for the highest
$\kappa$ lines of sight will be a better group and cluster model:
\citet{MomchevaEtal2006} and  \citet{WongEtal2011} recommend using models
where dark mass is assigned to both galaxy-scale halos and halos for the
groups and clusters they occupy: to make this work, one could incorporate  a
group and cluster finder, and then infer halo mass from optical richness
\citep[\eg][]{MaxBCG} in tandem with BCG stellar mass.

Interestingly, we have found that it is the most empty lines of sight that 
can be reconstructed with the highest precision. $\kappa$ estimates for empty
lines of sight receive few contributions from halos, and a large contribution
from voids; since they have the tightest PDFs after the reconstruction it
seems that our model's biggest uncertainties are driven by naively
reconstructing halos rather than neglecting voids. With a photometric
reconstruction of the field there is a significant broadening, but the
resulting precision is still typically 50\%  higher than using the global
$\kappa$ distribution.

@@

More generally, the method presented here is tied to the simulations at
several points: in particular, the prior PDF for $\kappah$, and the
conditional distribution $\pr(\kappa|\kappah)$ used to convert halo model
convergence to total convergence. The former tie could potentially be avoided
if the halo mass estimation gave rise to a reasonable $\pr(\kappah|\data)$ on
its own. Possibilities for improving the precision of the halo mass estimation
are discussed above. The latter tie is more difficult, since breaking it means
modelling the unseen mass structures and voids from first principles. It
should be possible to infer hierarchically  the parameters of a flexible model
for these things from the data itself, as demonstrated by
\citet{KarpenkaEtal2012} -- how much this dilutes the cosmographic precision
is to be investigated.  Including more information in this analysis is key:
weak lensing shears will be available over the whole Euclid and LSST survey
areas: fitting these with the halo models described here in order to constrain
the hyper-parameters of the model is an interesting
possibility.

@@

\item Despite our model's simplicity, its reconstructed $\kappah$ values are
good, if biased, tracers of $\kappa$.  We found that with perfect knowledge of
the halo mass and redshift (from the Millennium Simulation catalogs), for a
typical line of sight the calibrated reconstruction gives an unbiased estimate
of $\kappa$ that is a factor of 2 more precise than the global $\pr(\kappa)$.

@@

\item  For the most overdense lines of sight, the reconstruction produces a
very broad PDF; conversely, we find that the lines of sight with the sharpest
inferred $\pr(\kappa|\data)$ are typically under-dense. Since the
reconstructions described here can be performed before follow-up time is
invested, it will be possible to  select targets by the precision of their
$\kappa$ estimates. This procedure results in a sample with low bias as well
as high precision.

\item Photometric data is sufficient  to select the best lines of sight for
follow-up. Spectroscopic coverage helps to tighten  $\pr(\kappa|\data)$ for
high $\kappa$ lines of sight, but is of limited use for  low $\kappa$ lines of
sight.

\item It is very rare for halos further than 2 arcminutes from the line of
sight to make a significant contribution to $\pr(\kappa|\data)$. Including
halos whose host galaxy is less luminous than $i=24$ does not significantly
improve our reconstruction precision.  A photometric survey to this depth of a
4$\times$4 arcminute patch around the target would approach the limiting
uncertainties of our simple reconstruction recipe, and yield a 
$\pr(\kappa|\data)$ that has, on average, a width of 0.016. This is 1.5 times
less broad than the global $\pr(\kappa)$.

\item With only a photometric reconstruction of all time delay lens fields,
and following up only the systems with the most precise $\kappa$ estimates,
the width of the dominant statistical uncertainty in time-delay cosmography
can be halved, without inducing biases at the one percent level.

@@

External convergence is not the only uncertainty in time delay cosmology, but
for systems like B1608$+$656 it is the dominant one. For most lines of sight
it is likely that lens modelling induces uncertainties at the $\sim$3 percent
level, which far exceeds the typical $\kappa$ uncertainties after applying our
reconstruction \proceedure. By using our method to reconstruct lines of sight
and select which lense are followed-up, the uncertainties due to line of sight
convergence will become a sub-dominant  source of error.

### 2012-11-01 doc/references.tex
added citations to Karpenka et al

>>>>

\bibitem[J{\"o}nsson et al.(2010)]{JonssonEtal2010} J{\"o}nsson, J., 
Dahl{\'e}n, T., Hook, I., Goobar, A., M{\"o}rtsell, E.\ 2010, \mnras, 402, 526

\bibitem[Johnston et al.(2007)]{JohnstonEtal2007} Johnston, D.~E., 
Sheldon, E.~S., Wechsler, R.~H., et al.\ 2007, arXiv:0709.1159

\bibitem[Karpenka et al.(2012)]{KarpenkaEtal2012} Karpenka, N.~V., 
March, M.~C., Feroz, F., \& Hobson, M.~P.\ 2012, arXiv:1207.3708
